Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-27 writeup/gz_hubble_data.tex

\title{Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging}
%% Use \author, \affil, plus the \and command to format author and affiliation 
%% information.  If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.
%%
%% The \affil should be used to document primary affiliations and the
%% \altaffil should be used for secondary affiliations, titles, or email.

@@

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs
using the Advanced Camera for Surveys, with filters that probe the rest-frame
optical emission from galaxies out to $z\sim1$.  The bulk of the sample is
selected to have $m_{I814W}<23.5$ across AEGIS, COSMOS, GEMS, and 2-epoch
exposures in GOODS-N and GOODS-S. Full-depth 5-epoch images from the GOODS
fields are also included and have $m_{I814W}<26.8$. The median redshift of the
combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out to
$z\simeq4$. The GZH morphological data include measurements of both bulge- and
disk-dominated galaxies, details on spiral disk structure that relate to the
Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $150,771$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
\end{abstract}

@@

%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
GOODS images from both fields included galaxies with $m<26.8$. This yielded a
total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

\begin{table*}
\center
\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lllcrr}
\hline\hline
Survey &  Total $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8157    \\
COSMOS                                  & 2028         & \Iband{}                         & 0.05 & 6480               & 88530   \\
GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9143    \\
GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
\hspace{10pt} \emph{GOODS-N~2~epoch}    & 2100$-$4200  & \Vband, \iband                   & 0.03 & 320                & 2551    \\
\hspace{10pt} \emph{GOODS-S~2~epoch}    & 2100$-$4200  & \Vband, \zband                   & 0.03 & 320                & 3593    \\
\hspace{10pt} \emph{GOODS-N~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 6015    \\
\hspace{10pt} \emph{GOODS-S~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 5142    \\
\hline
total                                   & $-$          & $-$                              & $-$  & 8630 & 123131  \\
\hline\hline
\end{tabular}
\end{table*}

@@

The full GZH sample is composed of 7~different galaxy sub-samples. Throughout
this paper and in the published catalogs they are referred to with the
following labels:

@@

%\ref{tbl:catalog_hst}
\item \main: \hst{} imaging with RGB colors making use of all available
filters with typical saturation and in correct order, as described in
Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
full-depth GOODS (North and South) images. (118,425~galaxies)

@@

%ferengi <-- no table?
\item \redshifted: Simulated \hst{} images constructed using SDSS
images and artificially redshifted to between $0.3 \leq z \leq 1$. (288
original galaxies; 3,950~redshifted galaxies)

%\ref{tbl:simulated_agn}
\item \simagn: Simulated AGN host galaxies constructed using
\hst{} images and PSFs. (96~original galaxies; 2,961~simulated AGN host
galaxies)

@@

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH classifiers, labeled with
the corresponding Task numbers. Tasks in the decision tree are color-coded by
tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are
asked in every classification. Tasks colored green, blue, purple, and pink
(respectively) are one, two, three, or four steps below branching points in the
decision tree. The dashed line between T15 and T03 indicates the unique case
where volunteers could label both clumpy and disk-like morphologies for
galaxies with clumps arranged in a spiral pattern.}
\label{fig:decisiontree}
\end{figure*}

@@

In GZH, the redshift range is large enough that cosmological
evolution of the types and morphologies of galaxies is expected for the \hst{}
sample. As a result, the previous methods of correcting for
redshift-dependent bias do not work. In addition, the effects of band shifting
will change the images even more across these redshift ranges.

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images.  These are simulated images of a set of nearby galaxies as
they would appear observed at a variety of redshifts.  The input images are
from the SDSS \citep{yor00,str02}.  The sample consists of 288~nearby galaxies
at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
GZ2 classifications, including identifications of spiral structure,
ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
$r$-band surface brightnesses.  The overall selection spanned the
redshift range of SDSS targets and maximized the number of \hst{} galaxies at
the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
\ferengi{} code was used to produce sets of images corresponding to
observations of these galaxies out to $z_\mathrm{sim}=1.0$ (see
Section~\ref{ssec:ferengi}).  The resulting images were classified in the GZH
interface using the standard classification scheme.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/sb_redshift.pdf}
\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
values. The color histogram shows the number of \ferengi{} images as a function
of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
with contours starting at $N=1000$ and separated by intervals of 1000 up to
7000.} 
\label{fig:sb_redshift}
\end{center}
\end{figure}

@@

The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
$i$-band surface brightness ($\mu_\mathrm{i}$; intrinsic) and redshift ($z$;
extrinsic).

@@

Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
with Equation~\ref{eqn:fzeta}. Interestingly, the correction is only a weak
function of surface brightness. Higher-surface brightness galaxies have on
average slightly stronger corrections, possibly because these galaxies have
larger $f_\textrm{features}$ values at high redshifts. Low surface brightness
galaxies are more likely to begin low and remain low; the bounded nature of the
dropoff (and variance among the individual voters) means that the average
magnitude of $\zeta$ will be lower.

\begin{figure}
\center
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only galaxies with a bounded range on the dropoff
($-10<\log(\zeta)<10$) and sufficient points to fit each function (37~original
galaxies, each artificially redshifted to create a total of 296~images).}
\label{fig:zeta_mu}
\end{figure}

@@

\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
a function of surface brightness. The best-fit parameters to the linear fit
(from least-squares optimization) are $\zeta_0=0.75$, $\zeta_1=-.04$. To make the
final debiased correction, the simple exponential form of
Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions
between $f$ and 1:

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{Effects of redshift bias in 3,950~images in the \ferengi{} sample.
Each point \emph{in a given redshift and surface brightness bin} represents a
unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
image of that galaxy redshifted to the value corresponding to that redshift
bin. On the $x$-axis is the \ffeatures{} value of the image of the same galaxy
redshifted to $z=0.3$. The dashed black lines represent the best-fit
polynomials to the data in each square. The solid black line represents
\ffeaturesz=\ffeaturesrest. Regions in which there is a single-valued
relationship between \ffeatures{} at high redshift and at $z=0.3$ are white;
those in which there is not are blue, and those with not enough data ($N<5$)
are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu <
21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
\label{fig:f_vs_f}
\end{figure*}

@@

Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} for the \ferengi{}
galaxies relative to their lowest simulated redshift. This analysis only uses
galaxies whose lowest simulated redshift image was $z_\mathrm{sim}=0.3$ and
with detectable surface brightness measurements from \sextractor{} \citep{mel16}; this includes
3,950 of the total 6,466~images originally processed. For each simulated
redshift value \zsim{} at a fixed surface brightness $\mu$, \ffeaturesz, the
value measured at that simulated redshift, is plotted against \ffeaturesrest,
the value measured for the same galaxy at \zsim$=0.3$.

@@

\begin{table}
\center
\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}.
Correctable images have a single-valued relationship between their measured
\ffeatures{} values at high and low redshifts (white regions in
Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a
non single-valued relationship (blue regions). NEI (``not enough information'')
images have undetermined relationships due to a lack of data ($N<5$) in their
corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Lower-limit                        & 1,986   & 50\% \\
NEI                                & 80      &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrrrr}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
\hline
correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
no correction needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
not enough information (NEI)       & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
no redshift information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
\hline
total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}

@@

The catalog for GZH includes morphological data for 181,101~images
(generated from a total of 150,771~unique galaxies). The full table can be
accessed at \url{http://data.galaxyzoo.org}. The online data also includes a
secondary metadata table, which is drawn from a variety of sources detailed in
Section \ref{sec:data}.

@@

\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in
negative vote fractions for \fsmooth; these were cases in which the
\ffeatures{} vote fraction was boosted to a high value relative to \fartifact.
In these cases, the constraint of Equation~\ref{eqn:constraint} is met by
setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly. This correction is
typically small, with a median change of
\ffeatures{} or \fsmooth{} of $\Delta f = 0.04$.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images\label{tbl:stripe82_single}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594 &  0  \\
AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651 &  0  \\
AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043 &  0  \\
AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605 &  0  \\
AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &  1  \\
AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.5	    &    0.542  &   0.680   &   0.541 &  0  \\
AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &  0  \\
AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &  1  \\
AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.0	    &    0.0    &   0.0	    &   0.0   &  0  \\
AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &  0  \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 21,522~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

@@

Galaxies in GZH show significant changes in the disk/elliptical fraction as a
function of redshift, along with an increasing number of galaxies dominated by
smaller clumps and presumed to be in the process of building up their baryonic
mass through a combination of hierarchical merging and in-situ star formation.
While the majority of scientific interpretation is left to future work, this
paper confirms the decrease in observed bar fraction with increasing redshift
\citep{mel14} and identifies a new way for selecting clumpy galaxies as a
function of clump multiplicity.

>>>>

\title{Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging}
%% Use \author, \affil, plus the \and command to format author and affiliation 
%% information.  If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.
%%
%% The \affil should be used to document primary affiliations and the
%% \altaffil should be used for secondary affiliations, titles, or email.

@@

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs
using the Advanced Camera for Surveys, with filters that probe the rest-frame
optical emission from galaxies out to $z\sim1$.  The bulk of the sample is
selected to have $m_{I814W}<23.5$ across AEGIS, COSMOS, GEMS, and 2-epoch
exposures in GOODS-N and GOODS-S. Full-depth 5-epoch images from the GOODS
fields are also included and have $m_{I814W}<26.8$. The median redshift of the
combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out to
$z\simeq4$. The GZH morphological data include measurements of both bulge- and
disk-dominated galaxies, details on spiral disk structure that relate to the
Hubble type, bar identification, and numerous measurements of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $119,849$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
% Number = hubble + goods_shallow + stripe82_coadd
\end{abstract}

@@

%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth
GOODS images from both fields included galaxies with $m<26.8$. This yielded a
total of $119,849$~images (Table~\ref{tbl:gzh_numbers}).

@@

\begin{table*}
\center
\caption{Summary of GZH \hubble{} imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lllcrr}
\hline\hline
Survey &  Total $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8507    \\
COSMOS                                  & 2028         & \Iband{}                         & 0.05 & 6480               & 84954   \\
GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9087    \\
GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
\hspace{10pt} \emph{GOODS-N~2~epoch}    & 2100$-$4200  & \Vband, \iband                   & 0.03 & 320                & 2551    \\
\hspace{10pt} \emph{GOODS-S~2~epoch}    & 2100$-$4200  & \Vband, \zband                   & 0.03 & 320                & 3593    \\
\hspace{10pt} \emph{GOODS-N~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 6015    \\
\hspace{10pt} \emph{GOODS-S~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 5142    \\
\hline
all \hst{} surveys                      & $-$          & $-$                              & $-$  & 8630               & 119849  \\
\hline\hline
\end{tabular}
\end{table*}

@@

The full GZH sample is composed of 8~different galaxy sub-samples. Throughout
this paper and in the published catalogs they are referred to with the
following labels:

@@

%\ref{tbl:catalog_hst}
\item \main: \hst{} imaging with RGB colors making use of all available
filters with typical saturation and in correct order, as described in
Section~\ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and
full-depth GOODS (North and South) images. (113,705~galaxies)

@@

%ferengi <-- no table?
\item \redshifted: Simulated \hst{} images constructed using SDSS
images and artificially processed to redshifts between $0.3 \leq z \leq 1$.
(288~original galaxies; 6,624~redshifted images)

%\ref{tbl:simulated_agn}
\item \simagn: Simulated AGN host galaxies constructed using \hst{} images and
PSFs. (96~original galaxies; 2,961~images of simulated AGN hosts)

@@

The technique for redshift debiasing (Section~\ref{sec:debiasing}) requires
consistent measurements of the galaxy surface brightness. For both the
\redshifted{} calibration images and the \hst{} images which have their
morphologies corrected, we calculate the mean surface brightness $\mu$ within the
:w
effective radius ($R_e$) as:

\begin{equation}
\mu = m + 2.5*\log_{10}{(2 \times (b/a) \times \pi R_e^2 )}.
\label{eqn:surface_brightness}
\end{equation}

All photometric parameters are taken from \sextractor. For the \ferengi{}
galaxies, $m$ is {\tt MAG\_AUTO} in the \Iband{} band, $(b/a)$ is the galaxy
ellipticity (the profile RMS along the semi-major and -minor axes), and $R_e$
is the 50\% {\tt FLUX\_RADIUS} converted into arcsec \citep{mel16}. For the \hst{} galaxies in the \main{} sample,
the parameters are identical except that we use {\tt MAG\_BEST} instead of
{\tt MAG\_AUTO} \citep{gri12} in either the \Iband, \iband, or \zband{} bands, depending 
on the available imaging (Table~\ref{tbl:gzh_numbers}).

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH classifiers, labeled with
the corresponding task numbers. Tasks in the decision tree are color-coded by
tier level: Gray-colored tasks are 1$^\mathrm{st}$-tier questions which are
asked in every classification. Tasks colored green, blue, purple, and pink
(respectively) are one, two, three, or four steps below branching points in the
decision tree. The dashed line between T15 and T03 indicates the unique case
where volunteers could label both clumpy and disk-like morphologies for
galaxies with clumps arranged in a spiral pattern.}
\label{fig:decisiontree}
\end{figure*}

@@

In GZH, the redshift range is large enough that cosmological evolution of the
types and morphologies of galaxies is expected for the \hst{} sample. In
addition, the effects of band shifting will change the images even more across
these redshift ranges. As a result, the previous methods of correcting for
redshift-dependent bias do not work.

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images.  These are simulated images of a set of nearby galaxies as
they would appear observed at a variety of redshifts.  The input images are
from the SDSS \citep{yor00,str02}.  The sample consists of 288~well-resolved galaxies
at $z<0.013$. The galaxies spanned a variety of morphologies (as selected by
GZ2 classifications, including identifications of spiral structure,
ellipticals, mergers, edge-on disks, bulge prominence/shape, and bars) and
$r$-band surface brightnesses.  The overall selection spanned the
redshift range of SDSS targets and maximized the number of \hst{} galaxies at
the same surface brightness and redshift (Figure~\ref{fig:sb_redshift}).  The
\ferengi{} code was used to produce sets of images corresponding to
observations of these galaxies out to $z_\mathrm{sim}=1.0$ (see
Section~\ref{ssec:ferengi}).  The resulting images were classified in the GZH
interface using the standard classification scheme.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/sb_redshift.pdf}
\caption{Surface brightness as a function of redshift for 3,449~\ferengi{}
images and the 102,548~\main{} galaxies with measured $\mu$ and $z$ values. The
color histogram shows the number of \ferengi{} images as a function of $\mu$
and $z_{\rm sim}$. White contours show counts for the galaxies in the \main{}
sample, with the outermost contour starting at $N=1500$ and separated by
intervals of 1500.} 
\label{fig:sb_redshift}
\end{center}
\end{figure}

@@

The approach used in GZH for correcting the weighted classifications for
redshift bias rests on the assumption that the \emph{degree} of bias is a
function of the apparent size and brightness of the galaxy.
This is controlled by two types of parameters: \textbf{intrinsic} properties of
the galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. The combination of all
such parameters forms a high-dimensional space, and it is not clear how to
separate this into individual effects. Instead, the method used here employs
only two parameters as a simple model of the effect of redshift brightness on classification: the
surface brightness ($\mu$; intrinsic) and redshift ($z$;
extrinsic).

@@

Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
with Equation~\ref{eqn:fzeta}. This fit only includes galaxies where
\sextractor{} robustly measured the photometry in all images between
$0.3<z_\mathrm{sim}<1.0$ (such that $\sigma_{M_I}<1.0$~mag; \citealt{mel16}). Interestingly, the
derived correction is only a very weak function of surface brightness.
Higher-surface brightness galaxies have on average slightly stronger
corrections, possibly because these galaxies have larger $f_\textrm{features}$
values at high redshifts. Low surface brightness galaxies are more likely to
begin low and remain low; the bounded nature of the dropoff (and variance among
the individual voters) means that the average magnitude of $\zeta$ will be
lower.

\begin{figure}
\center
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only galaxies with a bounded range on the dropoff
($-10<\log(\zeta)<10$) and sufficient points to fit each function (37~original
galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
\label{fig:zeta_mu}
\end{figure}

@@

\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
a function of surface brightness. The best-fit parameters to the linear fit
(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
final debiased correction, the simple exponential form of
Equation~\ref{eqn:fzeta} is modified to bound the debiased vote fractions
between $f$ and 1:

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{Effects of redshift bias in 3,449~images in the \ferengi{} sample.
Each point \emph{in a given redshift and surface brightness bin} represents a
unique galaxy. On the $y$-axis in each bin is the \ffeatures{} value of the
image of that galaxy redshifted to the value corresponding to that redshift
bin. On the $x$-axis is the \ffeatures{} value of the image of the same galaxy
redshifted to $z=0.3$. The dashed black lines represent the best-fit
polynomials to the data in each square. The solid black line represents
\ffeaturesz=\ffeaturesrest. Regions in which there is a single-valued
relationship between \ffeatures{} at high redshift and at $z=0.3$ are white;
those in which there is not are blue, and those with not enough data ($N<5$)
are gray. A larger version of the bin outlined at $z=1.0$ and $20.3 < \mu <
21.0$ $\rm (mag/arcsec^2)$ is shown in Figure~\ref{fig:f_vs_f_zoom}.}
\label{fig:f_vs_f}
\end{figure*}

@@

Figure~\ref{fig:f_vs_f} shows the change in \ffeatures{} as a function of their
lowest simulated redshift for the 3,449~\ferengi{} images with robust photometric
measurements across the full range of redshifts.  For each simulated redshift
value \zsim{} at a fixed surface brightness, \ffeaturesz{} is the value
measured at that simulated redshift. We plot \ffeaturesz{} against \ffeaturesrest, the
value measured for the same galaxy at \zsim$=0.3$.

@@

\begin{table}
\center
\caption{Distribution of \ferengi{} images analyzed in Figure~\ref{fig:f_vs_f}.
Correctable images have a single-valued relationship between their measured
\ffeatures{} values at high and low redshifts (white regions in
Figure~\ref{fig:f_vs_f}). Images with only a lower-limit on \ffeatures{} have a
non single-valued relationship (blue regions). NEI (``not enough information'')
images have undetermined relationships due to a lack of data ($N<5$) in their
corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
                                   & N       & \% \\
\hline 
Correctable                        & 1,690   &  49\% \\
Lower-limit                        & 1,678   &  49\% \\
NEI                                & 81      &   2\%\\
Total                              & 3,449   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrr|r}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS  & GOODS-N & GOODS-S  &  Total  \\
                                   &                 &         &        &       & 5-epoch & 5-epoch  &         \\
\hline
correctable                        & 0               & 2,908   & 21,169 & 2,802 & 1,459   & 1,189    &  29,527 \\
lower-limit                        & 1               &   833   &  5,169 & 1,021 & 1,377   & 1,267    &   9,667 \\
no correction needed ($z \le 0.3$) & 2               &   955   & 10,870 & 1,175 &   415   &   400    &  13,815 \\ 
not enough information (NEI)       & 3               & 2,677   & 43,058 & 3,559 & 2,077   & 2,184    &  53,555 \\
no redshift information            & 4               & 1,134   &  4,688 &   530 &   687   &   102    &   7,141 \\
\hline
total                              &                 & 8,507   & 84,954 & 9,087 & 6,015   & 5,142    & 113,705 \\
\hline\hline
\end{tabular}
\end{table*}

@@

The catalog for GZH includes morphological data for 189,149~images
(generated from a total of 145,741~unique galaxies). The full table can be
accessed at \url{http://data.galaxyzoo.org}. The online data also includes a
secondary metadata table, which is drawn from a variety of sources detailed in
Section \ref{sec:data}. 
% 113705+6144+30339-4447 = 145,741
% main + goods_shallow + stripe82_coadd - goods_union

@@

\noindent In rare cases ($1.2\%$ of the \main{} sample), this requirement resulted in
negative vote fractions for \fsmooth; these were cases in which the
\ffeatures{} vote fraction was boosted to a high value relative to \fartifact.
In these cases, the constraint of Equation~\ref{eqn:constraint} is met by
setting \fsmooth$=0.0$ and decreasing \fbest{} accordingly. This correction is
typically small, with a median change of
\ffeatures{} or \fsmooth{} of $\Delta f = 0.04$.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for SDSS Stripe 82 single-epoch images\label{tbl:stripe82_single}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{5}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ5000001  &   587730845812064684  &   SDSS    &     2 &   41  &   0.585   &    0.595  &   0.759   &   0.594 &  0  \\
AHZ5000002  &   587730845812065247  &   SDSS    &     2 &   46  &   0.609   &    0.651  &   0.897   &   0.651 &  0  \\
AHZ5000003  &   587730845812196092  &   SDSS    &     2 &   51  &   0.039   &    0.044  &   0.067   &   0.043 &  0  \\
AHZ5000004  &   587730845812196825  &   SDSS    &     2 &   35  &   0.514   &    0.605  &   0.928   &   0.605 &  0  \\
AHZ5000005  &   587730845812524122  &   SDSS    &     2 &   47  &   0.766   &    0.812  &   1.038   &   0.810 &  1  \\
AHZ5000006  &   587730845812654984  &   SDSS    &     2 &   42  &   0.500   &    0.542  &   0.680   &   0.541 &  0  \\
AHZ5000007  &   587730845812655541  &   SDSS    &     2 &   41  &   0.488   &    0.526  &   0.697   &   0.525 &  0  \\
AHZ5000008  &   587730845812720365  &   SDSS    &     2 &   53  &   0.792   &    0.84   &   1.050   &   0.839 &  1  \\
AHZ5000009  &   587730845812720640  &   SDSS    &     4 &   43  &   0.000   &    0.0    &   0.000   &   0.0   &  0  \\
AHZ500000a  &   587730845812720699  &   SDSS    &     2 &   40  &   0.425   &    0.478  &   0.588   &   0.477 &  0  \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 21,522~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

@@

Galaxies in GZH show significant changes in the disk/elliptical fraction as a
function of redshift, along with an increasing number of galaxies dominated by
smaller clumps and presumed to be in the process of building up their baryonic
mass through a combination of hierarchical merging and in-situ star formation.
While the majority of scientific interpretation is left to future work, this
paper confirms the decrease in observed bar fraction with increasing redshift
and identifies a new way of selecting clumpy galaxies as a
function of clump multiplicity.
